Edge sign prediction in general graphs and Correlation Clustering

### 2017-09-12 troll/generative.tex
typo

The basic intuition is that the nature $\yuv$ of a relationship \euv{} is stochastically
determined by a mixture between how much node $u$ tends to like other people ($p_u$) and how much
node $v$ tends to be liked by other people ($q_v$). In a certain sense, $1-tr(u)$ is the empirical
counterpart to $p_u$, and $1-un(v)$ is the empirical counterpart to $q_v$. One might view
our model as reminiscent of standard models for link generation in social network analysis, like the
classical $p_1$ model from \cite{hl81}. However, note that the similarity falls short, for all these
models aim at
representing the likelihood of the network topology, rather than the probability of edge signs, once
the topology is \emph{given}.}

Notice that the Bayes optimal prediction for $\yuv$ is $y^*(u,v) = \sgn\big(\eta(u,v) -
\tfrac{1}{2}\big)$, where $\eta(u,v) = \Pr\big( \yuv = 1 \big)$. Moreover, the probability of
drawing at random a $+1$-labeled edge from $\Nout(u)$ equals
\begin{equation}\label{e:pout}
	\frac{1}{2}\,\Biggl(p_u + \frac{1}{\dout(u)} \sum_{v\in \nnout(u)} q_v \Biggl) =
		\frac{1}{2}\,\left(p_u + \qbar_u\right)\,,
\end{equation}
where $\qbar_u = \frac{1}{\dout(u)} \sum_{v\in \nnout(u)} q_v$ is the average $q$ value of $u$ out
neighbors.
Similarly, the probability of drawing at random a $+1$-labeled edge from $\Nin(v)$ equals
\begin{equation}\label{e:pin}
	\frac{1}{2}\,\Biggl(q_v + \frac{1}{\din(v)} \sum_{u\in \NNin(v)} p_u \Biggl)=
		\frac{1}{2}\,\left(q_v + \pbar_v\right)
\end{equation}

>>>>

The basic intuition is that the nature $\yuv$ of a relationship \euv{} is stochastically
determined by a mixture between how much node $u$ tends to like other people ($p_u$) and how much
node $v$ tends to be liked by other people ($q_v$). In a certain sense, $1-tr(u)$ is the empirical
counterpart to $p_u$, and $1-un(v)$ is the empirical counterpart to $q_v$. One might view
our model as reminiscent of standard models for link generation in social network analysis, like the
classical $p_1$ model from \cite{hl81}. However, note that the similarity falls short, for all these
models aim at
representing the likelihood of the network topology, rather than the probability of edge signs, once
the topology is \emph{given}.

Notice that the Bayes optimal prediction for $\yuv$ is $y^*(u,v) = \sgn\big(\eta(u,v) -
\tfrac{1}{2}\big)$, where $\eta(u,v) = \Pr\big( \yuv = 1 \big)$. Moreover, the probability of
drawing at random a $+1$-labeled edge from $\Nout(u)$ equals
\begin{equation}\label{e:pout}
	\frac{1}{2}\,\Biggl(p_u + \frac{1}{\dout(u)} \sum_{v\in \NNout(u)} q_v \Biggl) =
		\frac{1}{2}\,\left(p_u + \qbar_u\right)\,,
\end{equation}
where $\qbar_u = \frac{1}{\dout(u)} \sum_{v\in \NNout(u)} q_v$ is the average $q$ value of $u$ out
neighbors.
Similarly, the probability of drawing at random a $+1$-labeled edge from $\Nin(v)$ equals
\begin{equation}\label{e:pin}
	\frac{1}{2}\,\Biggl(q_v + \frac{1}{\din(v)} \sum_{u\in \NNin(v)} p_u \Biggl)=
		\frac{1}{2}\,\left(q_v + \pbar_v\right)
\end{equation}
